\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-03-13 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
replaced the OCEANS flag with APPROXIMATE_OCEAN_LOAD to avoid confusion

\item [{\texttt{OCEANS}}] Set to \texttt{.true.} if the effect of the oceans

@@

approximate treatment discussed in \citet{KoTr02b}. This feature

@@

phases/reverberations is not taken into account, even when the flag
is on.
\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{OCEANS} is set to \texttt{.true.}.

>>>>

\item [{\texttt{APPROXIMATE\_OCEAN\_LOAD}}] Set to \texttt{.true.} if the effect of the oceans

@@

(rough) approximate treatment discussed in \citet{KoTr02b}. This feature

@@

phases/reverberations is not taken into account, even when the flag is on.
\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{APPROXIMATE\_OCEAN\_LOAD} is set to \texttt{.true.}.
